BlogForever Crawler: Techniques and Algorithms\\to Harvest Modern Weblogs

### 2014-04-14 tex/runningtimeFigure.tex
Place caption below figure 2

\begin{figure}[t]
  \capstart
  \refstepcounter{figure}
  \label{runningtime}
  \vspace{-12pt}
  \hspace{-34pt}
  \begin{gnuplot}% nop
    set terminal epslatex color
    set size 0.76
    set size ratio 0.618

    set title '\textbf{Figure \arabic{figure}: Running time of article extraction}'
    set ylabel 'Cumulated running time (sec.)' offset 1.3
    set xlabel 'Processed blog posts'

@@

    plot 'data/runningtime.txt'\
       u 0:1 smooth cumulative w lines linewidth 3 title 'Our approach',\
    '' u 0:4 smooth cumulative w lines linewidth 4 title 'Readability',\
    '' u 0:2 smooth cumulative w lines linewidth 4 title 'Boilerpipe',\
    '' u 0:3 smooth cumulative w lines linewidth 4 title 'Goose'
  \end{gnuplot}
  \vspace{-12pt}
\end{figure}

>>>>

\begin{figure}[t]
  \refstepcounter{figure}
  \label{runningtime}
  \vspace{-12pt}
  \hspace{-34pt}
  \begin{gnuplot}% nop
    set terminal epslatex color
    set size 0.75
    set size ratio 0.618

    set ylabel 'Cumulated running time (sec.)' offset 1.3
    set xlabel 'Processed blog posts'

@@

    plot 'data/runningtime.txt'\
       u 0:1 smooth cumulative w lines linewidth 3 title 'Our approach',\
    '' u 0:4 smooth cumulative w lines linewidth 4 title 'Readability',\
    '' u 0:2 smooth cumulative w lines linewidth 4 title 'Boilerpipe',\
    '' u 0:3 smooth cumulative w lines linewidth 4 title 'Goose'
  \end{gnuplot}
  \vspace{-18pt}
  \caption{Running time of article extraction.}
\end{figure}
